Usage metrics

### 2020-12-16 analysis/usage.Rmd

C_raw -> C
corpus_size <- nrow(P)
overview_table(
  r("Corpus",corpus_size)
) 
```

The size of our corpus is `corpus_size` packages.

@@

@@

TBL <- overview_table(
  # Sites triggered over the whole corpus:
  r("nb eval call sites", sites),
  # How many packages in the corpus have a single triggered call site:
  r("nb one call site", sites_per_package %>% filter(n == 1)),
  r("at least one call site", sites_per_package),
  r("packages no calls to eval", corpus_size - nrow(sites_per_package)),
  r("nb median call sites", median(sites_per_package$n)),
  r("max call sites", max_packages),
)
```

@@

```{r nb-eval-calls}
# run = package?
eval_calls_per_package <- E %>%
  count(ev_package, wt = duplicates) %>%
  left_join(runs_package, by = "ev_package") %>%
  mutate(n = n / nb_runs)

>>>>

C_raw -> C
corpus_size <- nrow(P)

nb_runs <- E %>%
  pull(file) %>%
  n_distinct()
overview_table(
  r("Corpus",corpus_size),
  r("NbRuns", nb_runs)
) 
```

The size of our corpus is `r corpus_size` packages.

@@

```{r ev-call-precise}

more_1000_calls <- eval_calls_table %>% filter(n > 1000) %>% nrow()

overview_table(
  r("eval calls less hundred", ev_summary[[1]] + ev_summary[[2]]),
  r("eval calls more thousand", more_1000_calls)
)
```

@@

TBL <- overview_table(
  # Sites triggered over the whole corpus:
  r("nb eval call sites", sites),
  # How many packages in the corpus have a single triggered call site:
  r("nb one call site", sites_per_package %>% filter(n == 1)),
  r("at least one call site", sites_per_package$n),
  r("packages no calls to eval", corpus_size - nrow(sites_per_package)),
  r("nb median call sites", median(sites_per_package$n)),
  r("max call sites", max_packages),
)
```

@@

```{r nb-eval-calls}
# run = package?
eval_calls_per_package <- E %>%
  count(ev_package, wt = duplicates) %>%
  left_join(runs_package, by = "ev_package")
